Coherent optical association of a single molecule -- Supplemental material

### 2020-11-25 sm.tex
Update SM caption

\begin{figure}[ht!]
  \includegraphics[width=\textwidth]{imgs/raman_theory_full.pdf}
  \caption{ Full calculation of the Raman Rabi frequency and scattering rate as a function of the single-photon frequency including all vibrational states of $ \mathrm{c^3\Sigma^+(\Omega = 1)}$ and the atomic continuum. The second frequency in the Raman transition is offset by about $770~\mathrm{MHz}$ and resonant with the two photon transition. The assumed excited-state linewidth for all molecular lines is $50~\text{MHz} $.
    \label{f-sm}}
\end{figure}

>>>>

\begin{figure}[ht!]
  \includegraphics[width=\textwidth]{imgs/raman_theory_full.pdf}
  \caption{Full calculation of the Raman Rabi frequency and scattering rate
    as a function of the single-photon frequency
    including all vibrational states of $ \mathrm{c^3\Sigma^+(\Omega = 1)}$
    and the atomic continuum.
    The second frequency in the Raman transition is offset by about $770~\mathrm{MHz}$
    and resonant with the two photon transition.
    The assumed excited-state linewidth for all molecular lines is $50~\text{MHz}$.
    The thick red line shows the contribution that comes only from the near-threshold states.
    \label{f-sm}}
\end{figure}
